--- 
title: "my_project"
subtitle: "Early draft, please do not share"
thanks: "For helpful comments we thank ..."
author: 
- Rafael Felipe Bressan[^eesp]
date: "Last update: `r Sys.Date()`"
abstract: "This paper explores a ... \\newline\\newline \\textbf{keywords}: tax evasion, customs duties, non-tariff barriers, trading companies"
site: bookdown::bookdown_site
documentclass: article
papersize: a4
fontsize: 12pt
geometry: "left=2.5cm,right=2.5cm,top=2cm,bottom=2cm"
bibliography: [references.bib]
biblio-style: authoryear
link-citations: yes
urlcolor: blue
citecolor: blue
github-repo: rfbressan/my_project
description: "My project description"
---

[^eesp]: Sao Paulo School of Economics, FGV/EESP

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center", 
  fig.retina = 3,
  fig.width = 7,
  out.width = "80%",
  fig.asp = 9/16
)
#' Remember, the working directory for code chunks is my_project/Article by 
#' default. Because we are using the targest package, which must be in the
#' project root, we set the working directory via root.dir in opts_knit$set()
knitr::opts_knit$set(
  root.dir = here::here())
```

```{r libraries, message=FALSE}
library(kableExtra)
library(data.table)
library(fst)
```

```{r load-ad-summary}
targets::tar_load("hello_vec")
```


# Introduction

The original character string processed is: "`r hello_vec`". 

Citations follow the [Rmarkdown](https://bookdown.org/yihui/rmarkdown/markdown-syntax.html) syntax as in
@arbex2015optimal or, [@arbex2015optimal]. In Table \@ref(tab:hello) we present the number of characters in the original string.

\input{Tables/hello}

Figure \@ref(fig:graph) shows the dependency structure of the current pipeline.

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{Figs/graph.png}
    \caption{Targets dependency graph}
    \label{fig:graph} 
\end{figure}
